---
title: "`r markdownTitle`"
author: ''
date: ''
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## {.tabset .tabset-fade}

<div align="center">
### Total Precipitation by Year
```{r,results='asis', echo=FALSE}

  p1<-ggplot(tempTable, aes(x=Year,y=`Total Precip (in)`, fill=`Missing Precip (days)`))+
        geom_bar(stat = 'identity',show.legend = FALSE)+
        scale_fill_gradient(low = "#004529", high = "#addd8e")+
        geom_hline(yintercept = mean(tempTable$`Total Precip (in)`))
        
      ggplotly(p1)
```
Total Precipitation by Year (Seasonal or Annual/Water Year)  
(Color indicates number of missing days, horizontal line is long-term mean)


### Avg Temperature by Year
```{r,results='asis', echo=FALSE}
  p2<-ggplot(tempTable, aes(x=Year,y=`Avg Temp (F)`))+
        geom_line()+
        geom_point(aes(color=`Missing Temp (days)`),show.legend = FALSE)+
        scale_color_gradient(low = "yellow", high = "red")+
        geom_hline(yintercept = mean(tempTable$`Avg Temp (F)`))
      ggplotly(p2)
```
Average Temperature by Year (Seasonal or Annual/Water Year)  
(Color indicates number of missing days, horizontal line is long-term mean)

### Daily Cumulative Precip
```{r,results='asis', echo=FALSE}
    ggplotly(pCum)
```
CAUTION: Cumulative totals in some years may include missing days and be artificially low

### Daily Min/Max Temps
```{r,results='asis', echo=FALSE}
    ggplotly(pTemps)
```

### Station Map
```{r,results='asis', echo=FALSE}
leaflet(width="100%") %>% addProviderTiles(providers$Esri.WorldTopoMap) %>%
  setView(stationLatLon$lon, stationLatLon$lat, zoom = 8) %>%
  addMarkers(lng=stationLatLon$lon, lat=stationLatLon$lat, popup=stationName)
```
</div>

------
```{r,results='asis', echo=FALSE}
kable(tempMean, caption="Period of Record Averages")
```
------

## {.tabset .tabset-fade}

<div align="center">
### Summary Stats
```{r,results='asis', echo=FALSE}
datatable(tempTable, class = 'cell-border compact stripe', escape = FALSE, rownames = FALSE,
          options = list(pageLength = 10, info = FALSE, lengthMenu = list(c(-1,10,50,100), c("All","10","50","100"))))
```

### Anomalies
```{r,results='asis', echo=FALSE}
datatable(tempAnom, class = 'cell-border compact stripe', escape = FALSE, rownames = FALSE,
           options = list(pageLength = 10, info = FALSE, lengthMenu = list(c(-1,10,50,100), c("All","10","50","100"))))
```

</div>

------
<div align="center">
  [Return to main page](https://cals.arizona.edu/climate/misc/stations/index.html)
</div>

<div align="center">
  <em>[Climate Science Applications Program - University of Arizona Cooperative Extension](http://cals.arizona.edu/climate/)</em>
</div>

<div align="center">
  <h6>
  Last Updated: "`r format(Sys.time(), '%m-%d-%Y')`"© 2020 The Arizona Board of Regents. All contents copyrighted. All rights reserved.</h6>
</div>


